---
title: ""
header-includes:
- \usepackage{caption}
- \captionsetup[figure]{labelformat=empty}
params:
  name: NA
  prepared_by: NA
  mult: NA
  alpha: NA
  omega_c: NA
  omega_h: NA
  omega_q: NA
  rho_s: NA
  rho_a: NA
  R: NA
  kappa: NA
  eta: NA
  nu: NA
  generation: NA
  t_ps: NA
  t_pa: NA
  t_qcs: NA
  t_qca: NA
  t_qhs: NA
  t_qha: NA
  t_q: NA
  mult_b: NA
  alpha_b: NA
  omega_c_b: NA
  omega_h_b: NA
  omega_q_b: NA
  rho_s_b: NA
  rho_a_b: NA
  R_b: NA
  kappa_b: NA
  eta_b: NA
  nu_b: NA
  t_ps_b: NA
  t_pa_b: NA
  t_qcs_b: NA
  t_qca_b: NA
  t_qhs_b: NA
  t_qha_b: NA
  t_q_b: NA
  generation_b: NA
---

```{r, include=FALSE}
  knitr::opts_chunk$set(echo = FALSE, dev = "png",
                        dev.args = list(type = "cairo-png"))
  knitr::opts_knit$set(eval.after = "fig.cap")

  fig_counter <- 1
  
  p <- params[-grep("_b", names(params))]
  p <- p[-1] # removing name
  p$t_p <- p$t_ps * (1 - p$alpha) + p$t_pa * p$alpha
  p$t_qh <- p$t_qhs * (1 - p$alpha) + p$t_qha * p$alpha
  p$t_qc <- p$t_qcs * (1 - p$alpha) + p$t_qca * p$alpha
  p$offset <- -2.31
  p$rate <- 0.5
  
  pB <- params[grep("_b", names(params))]
  pB <- pB[-1] # removing "generated_by"
  names(pB) <- gsub("_b", "", names(pB))
  pB$t_p <- pB$t_ps * (1 - pB$alpha) + pB$t_pa * pB$alpha
  pB$t_qh <- pB$t_qhs * (1 - pB$alpha) + pB$t_qha * pB$alpha
  pB$t_qc <- pB$t_qcs * (1 - pB$alpha) + pB$t_qca * pB$alpha
  pB$offset <- -2.31
  pB$rate <- 0.5
  
  pqc <- function(input=p){
    return(
    get_pqc_equilibrium(
      alpha = input$alpha,
      omega_c = input$omega_c,
      omega_h = input$omega_h,
      omega_q = input$omega_q,
      rho_s = input$rho_s,
      rho_a = input$rho_a,
      R = input$R,
      kappa = input$kappa,
      eta = input$eta,
      nu = input$nu,
      t_ps = input$t_ps,
      t_pa = input$t_pa,
      t_qcs = input$t_qcs,
      t_qca = input$t_qca,
      t_qhs = input$t_qhs,
      t_qha = input$t_qha,
      t_q = input$t_q,
      shape = as.numeric(input$generation)
    ))
  }
  
  r_eff <-function(input=p){
    return(get_r_effective(pqc(input),
            alpha = input$alpha,
            R = input$R,
            kappa = input$kappa,
            eta = input$eta,
            nu = input$nu,
            t_ps = input$t_ps,
            t_pa = input$t_pa,
            t_qcs = input$t_qcs,
            t_qca = input$t_qca,
            t_qhs = input$t_qhs,
            t_qha = input$t_qha,
            t_q = input$t_q,
            shape = as.numeric(input$generation))
    )
  }

```

## `r if(params$name == "") "Contact Tracing Program Evaluation" else {glue("Contact Tracing Program Evaluation: ", "{params$name}")}`

### `r if (!(params$prepared_by == "")) {glue("Prepared by: {params$prepared_by}")}`

*Report automatically generated from the [ConTESSA application](https://iddynamics.jhsph.edu/apps/connect/contessa/) on `r Sys.Date()`*

This report provides estimates of the effectiveness of two specified contact tracing programs (Scenarios A and B), based on key indicators for the timing and completeness of contact tracing.

### Program Assumptions

| Parameter                  | Value                    |  Value: Scenario B       |
|:---------------------------|:-------------------------|:-------------------------|
| **Surveillance**           |                          |                          |
| Percent of symptomatic infections isolated who were not identified during contact tracing | `r glue("{round(p$rho_s*100, 1)}", "%")`     | `r ifelse(p$rho_s == pB$rho_s, glue("-"), glue("{round(pB$rho_s*100, 1)}", "%"))`  |
| Percent of asymptomatic infections isolated who were not identified during contact tracing | `r glue("{round(p$rho_a*100, 1)}", "%")`     |  `r ifelse(p$rho_a == pB$rho_a, glue("-"), glue("{round(pB$rho_a*100, 1)}", "%"))`   |
| Average number of days between symptom onset and isolation of a detected case | `r glue("{p$t_p}")`     | `r ifelse(p$t_p == pB$t_p, glue("-"), glue("{pB$t_p}"))`    |
| **Household Contact Tracing**            |                           |                           |
| Percent of household contacts traced and quarantined | `r glue("{round(p$omega_h*100, 1)}", "%")`     |  `r ifelse(p$omega_h == pB$omega_h, glue("-"), glue("{round(pB$omega_h*100,1)}", "%"))`  |
| Average number of days between symptom onset of a symptomatic index case and household contacts notified and quarantined | `r glue("{p$t_qhs}")`     | `r ifelse(p$t_qh == pB$t_qh, glue("-"), glue("{pB$t_qh}"))`  |
| **Community Contact Tracing**            |                           |                           |
| Percent of community contacts traced and quarantined | `r glue("{round(p$omega_c*100, 1)}", "%")`     |   `r ifelse(p$omega_c == pB$omega_c, glue("-"), glue("{round(pB$omega_c*100, 1)}", "%"))`  |
| Average number of days between symptom onset of a symptomatic index case and community contacts notified and quarantined | `r glue("{p$t_qcs}")`     | `r ifelse(p$t_qc == pB$t_qc, glue("-"), glue("{pB$t_qc}"))`  |
| **Natural History and Transmission**  |                           |                           |
| Basic reproductive number $R_0$       | `r glue("{p$R}")`     |  --                         |
| Percent asymptomatic     | `r glue("{round(p$alpha*100,1)}", "%")`     |  --                         |
| Relative risk of transmission for an asymptomatic individual compared to a symptomatic individual |  `r glue("{round(p$kappa, 2)}")`     | --                         |
| Percent of all contacts that occur in the household |  `r glue("{round(p$eta*100, 1)}", "%")`     | `r ifelse(p$eta == pB$eta, glue("-"), glue("{round(pB$eta*100,1)}", "%"))`  |
| Relative risk of infection for a household contact compared to a community contact |  `r glue("{p$nu}")`     | --                         |

*Note that Scenario B values are only shown where they differ from Scenario A. Natural History assumptions can be modified in the "Advanced Options" module of the interactive application.*

### Effectiveness of Contact Tracing

```{r reductions}
  valA <- r_eff(input=p)
  redA <- (p$R - valA)/p$R
  percQ_A <- get_prop_identified(pqc(input=p))
  
  valB <- r_eff(input=pB)
  redB <- (p$R - valB)/p$R
  percQ_B <- get_prop_identified(pqc(input=pB))
  
  redA_refB <- (valB - valA)/valB
  redB_refA <- (valA - valB)/valA

  red_str <- ifelse(valB>valA,
                    glue("Scenario A therefore represents a further ", "{round((redA - redB)*100, 1)}", "% reduction in the reproductive number, compared to Scenario B."),
                    glue("Scenario B therefore represents a further ", "{round((redB - redA)*100, 1)}", "% reduction in the reproductive number, compared to Scenario A."))
```

**The contact tracing program following the assumptions listed above for Scenario A would be expected to reduce the reproductive number, $R$, from `r glue("{round(p$R,1)}")` to `r glue("{round(valA,1)}")`. This program is identifying `r glue("{round(percQ_A*100, 1)}", "%")` of infections in the community.**

**The contact tracing program following the assumptions listed above for Scenario B would be expected to reduce the reproductive number, $R$, from `r glue("{round(p$R,1)}")` to `r glue("{round(valB,1)}")`. This program is identifying `r glue("{round(percQ_B*100, 1)}", "%")` of infections in the community.**

**`r glue("{red_str}")`**

### Surveillance

```{r surv plot, fig.cap = cap, fig.width=6, fig.height=5}

  grid <- expand.grid(
        alpha = p$alpha,
        R = p$R,
        kappa = p$kappa,
        eta = p$eta,
        nu = p$nu,
        t_ps = p$t_ps,
        t_pa = p$t_pa,
        t_qcs = p$t_qcs,
        t_qca = p$t_qca,
        t_qhs = p$t_qhs,
        t_qha = p$t_qha,
        t_q = p$t_q,
        omega_c = p$omega_c,
        omega_h = p$omega_h,
        omega_q = p$omega_q,
        rho_s = seq(0, 1, 0.01),
        rho_a = 1,
        offset = p$offset,
        shape = as.numeric(p$generation),
        rate = p$rate
      )

  grid <- grid %>%
      mutate(rho_a = rho_s * p$mult)
    
  d <- pmap_df(grid, tti:::get_r_effective_df_one)
  d <- d %>%
      mutate(
        pct_detect = (rho_s * (1 - alpha) + rho_a * alpha)*100,
        t = t_ps * (1 - alpha) + t_pa * alpha
      )

  you_are_here <- tibble(
      x = (p$rho_s * (1 - p$alpha) + p$rho_a * p$alpha)*100,
      y = r_eff(p),
      name = "You are here"
    )
    
  
  grid_b <- expand.grid(
        alpha = pB$alpha,
        R = pB$R,
        kappa = pB$kappa,
        eta = pB$eta,
        nu = pB$nu,
        t_ps = pB$t_ps,
        t_pa = pB$t_pa,
        t_qcs = pB$t_qcs,
        t_qca = pB$t_qca,
        t_qhs = pB$t_qhs,
        t_qha = pB$t_qha,
        t_q = pB$t_q,
        omega_c = pB$omega_c,
        omega_h = pB$omega_h,
        omega_q = pB$omega_q,
        rho_s = seq(0, 1, 0.01),
        rho_a = 1,
        offset = pB$offset,
        shape = as.numeric(p$generation),
        rate = pB$rate
      )
  grid_b <- grid_b %>%
      mutate(rho_a = rho_s * pB$mult)
    
  d_b <- pmap_df(grid_b, tti:::get_r_effective_df_one)
  d_b <- d_b %>%
      mutate(
        pct_detect = (rho_s * (1 - alpha) + rho_a * alpha)*100,
        t = t_ps * (1 - alpha) + t_pa * alpha
      )

  you_are_here_b <- tibble(
      x = (pB$rho_s * (1 - pB$alpha) + pB$rho_a * pB$alpha)*100,
      y = r_eff(pB),
      name = "You are here"
    )
  
  d <- d %>% mutate(scn = "Scenario A") %>%
       bind_rows(d_b %>% mutate(scn = "Scenario B")) %>%
       mutate(scn_factor = factor(scn, levels=c("Scenario A", "Scenario B")))
  you_are_here <- you_are_here %>% mutate(scn = "Scenario A") %>%
       bind_rows(you_are_here_b %>% mutate(scn = "Scenario B")) %>%
       mutate(scn_factor = factor(scn, levels=c("Scenario A", "Scenario B")))
  
  pSurv <- ggplot(d, aes(x = pct_detect, y = r_effective, group = scn_factor, color=scn_factor)) +
      geom_line(size=0.8) +
      scale_color_manual(values = c("#4278cf", "#16916c")) +
      geom_point(data=you_are_here, aes(x=x, y=y), pch=21, cex=1.5, stroke=1.25, bg="#ffffff") +
      geom_hline(yintercept=1, lty=2) +
      geom_hline(yintercept=p$R, lwd=0.5) +
      ggtitle("Impact of the completeness of case isolation \non the reproductive number") +
      scale_y_continuous(name = "R", limits = c(min(c(1, d$r_effective)), max(c(d$r_effective, p$R)))) +
      scale_x_continuous(name = "Percent of infections isolated who were not identified during contact tracing") +
      theme_hc()
      
  pSurv
      
  cap <- paste0("**Figure ", fig_counter, "**: Impact of completeness of case isolation, as the percent of cases which were not identified during contact tracing and isolated, on the reproductive number, assuming that infections are isolated on average ", round(p$t_p, 1), " days after symptom onset in Scenario A. The filled circles represent the reproductive number for Scenarios A and B, described above. The lines represents the reproductive number if the percent of infections identified and isolated is changed, while all other assumptions for each scenario remain constant. The solid black line represents the reproductive number if there were no contact tracing program, and the dashed black line represents a reproductive number of 1, below which an epidemic would be expected to no longer grow.")
  fig_counter <- fig_counter + 1

```

```{r surv delay plot, fig.cap = cap, fig.width=6, fig.height=5}

  diff <- p$t_pa - p$t_ps 
  
  if (p$t_ps <= p$t_pa) { 
     t_ps <- seq(0, 14, 0.5) 
  } else { 
     t_ps <- seq((p$t_ps - p$t_pa), (14 + (p$t_ps - p$t_pa)), 0.5) 
  }

  grid <- expand.grid(
        alpha = p$alpha,
        R = p$R,
        kappa = p$kappa,
        eta = p$eta,
        nu = p$nu,
        t_ps = t_ps,
        t_pa = 1,
        t_qcs = p$t_qcs,
        t_qca = p$t_qca,
        t_qhs = p$t_qhs,
        t_qha = p$t_qha,
        t_q = p$t_q,
        omega_c = p$omega_c,
        omega_h = p$omega_h,
        omega_q = p$omega_q,
        rho_s = p$rho_s,
        rho_a = p$rho_a,
        offset = p$offset,
        shape = as.numeric(p$generation),
        rate = p$rate
      )

  grid <- grid %>%
      mutate(t_pa = t_ps + diff)
    
  d <- pmap_df(grid, tti:::get_r_effective_df_one)
  d <- d %>%
      mutate(
        t = t_ps * (1 - alpha) + t_pa * alpha
      )

  you_are_here <- tibble(
      x = p$t_ps * (1 - p$alpha) + p$t_pa * p$alpha,
      y = r_eff(p),
      name = "You are here"
    )
  
    
  diff_b <- pB$t_pa - pB$t_ps
  
  if (pB$t_ps <= pB$t_pa) { 
     t_ps_b <- seq(0, 14, 0.5) 
  } else { 
     t_ps_b <- seq((pB$t_ps - pB$t_pa), (14 + (pB$t_ps - pB$t_pa)), 0.5) 
  }
  
  grid_b <- expand.grid(
        alpha = pB$alpha,
        R = pB$R,
        kappa = pB$kappa,
        eta = pB$eta,
        nu = pB$nu,
        t_ps = t_ps_b,
        t_pa = 1,
        t_qcs = pB$t_qcs,
        t_qca = pB$t_qca,
        t_qhs = pB$t_qhs,
        t_qha = pB$t_qha,
        t_q = pB$t_q,
        omega_c = pB$omega_c,
        omega_h = pB$omega_h,
        omega_q = pB$omega_q,
        rho_s = pB$rho_s,
        rho_a = pB$rho_a,
        offset = pB$offset,
        shape = as.numeric(p$generation),
        rate = pB$rate
      )
  grid_b <- grid_b %>%
      mutate(t_pa = t_ps + diff_b)
    
  d_b <- pmap_df(grid_b, tti:::get_r_effective_df_one)
  d_b <- d_b %>%
      mutate(
        t = t_ps * (1 - alpha) + t_pa * alpha
      )

  you_are_here_b <- tibble(
      x = pB$t_ps * (1 - pB$alpha) + pB$t_pa * pB$alpha,
      y = r_eff(pB),
      name = "You are here"
    )
  
  d <- d %>% mutate(scn = "Scenario A") %>%
       bind_rows(d_b %>% mutate(scn = "Scenario B")) %>%
       mutate(scn_factor = factor(scn, levels=c("Scenario A", "Scenario B")))
  you_are_here <- you_are_here %>% mutate(scn = "Scenario A") %>%
       bind_rows(you_are_here_b %>% mutate(scn = "Scenario B")) %>%
       mutate(scn_factor = factor(scn, levels=c("Scenario A", "Scenario B")))
  
  pSurvDelay <- ggplot(d, aes(x = t, y = r_effective, group = scn_factor, color=scn_factor)) +
      geom_line(size=0.8) +
      scale_color_manual(values = c("#4278cf", "#16916c")) +
      geom_point(data=you_are_here, aes(x=x, y=y), pch=21, cex=1.5, stroke=1.25, bg="#ffffff") +
      geom_hline(yintercept=1, lty=2) +
      geom_hline(yintercept=p$R, lwd=0.5) +
      ggtitle("Impact of the delay from symptom onset to isolation \non the reproductive number") +
      scale_y_continuous(name = "R", limits = c(min(c(1, d$r_effective)), max(c(d$r_effective, p$R)))) +
      scale_x_continuous(name = "Days from symptom onset to isolation") +
      theme_hc() 
      
  pSurvDelay
      
  cap <- paste0("**Figure ", fig_counter, "**: Impact of timing of case isolation, as the delay from symptom onset, on the reproductive number, assuming that ", round(p$p_s*100), "% of cases are detected and isolated in Scenario A. The filled circles represent the reproductive number for Scenarios A and B, described above. The lines represents the reproductive number if the average time between symptom onset and ccase isolation is changed, while all other assumptions in each scenario remain constant. The solid black line represents the reproductive number if there were no contact tracing program, and the dashed black line represents a reproductive number of 1, below which an epidemic would be expected to no longer grow.")
  fig_counter <- fig_counter + 1

```

### Impact of Household Contact Tracing

```{r hh contact plot, fig.cap=cap, fig.width=6, fig.height=5}

  grid <- expand.grid(
      alpha = p$alpha,
      R = p$R,
      kappa = p$kappa,
      eta = p$eta,
      nu = p$nu,
      t_ps = p$t_ps,
      t_pa = p$t_pa,
      t_qcs = p$t_qcs,
      t_qca = p$t_qca,
      t_qhs = p$t_qhs,
      t_qha = p$t_qha,
      t_q = p$t_q,
      omega_c = p$omega_c,
      omega_h = seq(0, 1, 0.01),
      omega_q = p$omega_q,
      rho_s = p$rho_s,
      rho_a = p$rho_a,
      offset = p$offset,
      shape = as.numeric(p$generation),
      rate = p$rate
    )
  
  d <- pmap_df(grid, tti:::get_r_effective_df_one) %>%
        mutate(omega_h_pct = omega_h*100)

  you_are_here <- tibble(
      x = p$omega_h*100,
      y = r_eff(p),
      name = "You are here"
    )

  
  grid_b <- expand.grid(
      alpha = pB$alpha,
      R = pB$R,
      kappa = pB$kappa,
      eta = pB$eta,
      nu = pB$nu,
      t_ps = pB$t_ps,
      t_pa = pB$t_pa,
      t_qcs = pB$t_qcs,
      t_qca = pB$t_qca,
      t_qhs = pB$t_qhs,
      t_qha = pB$t_qha,
      t_q = pB$t_q,
      omega_c = pB$omega_c,
      omega_h = seq(0, 1, 0.01),
      omega_q = pB$omega_q,
      rho_s = pB$rho_s,
      rho_a = pB$rho_a,
      offset = pB$offset,
      shape = as.numeric(p$generation),
      rate = pB$rate
    )
  
  d_b <- pmap_df(grid_b, tti:::get_r_effective_df_one) %>%
        mutate(omega_h_pct = omega_h*100)

  you_are_here_b <- tibble(
      x = pB$omega_h*100,
      y = r_eff(pB),
      name = "You are here"
    )
  
  d <- d %>% mutate(scn = "Scenario A") %>%
       bind_rows(d_b %>% mutate(scn = "Scenario B")) %>%
       mutate(scn_factor = factor(scn, levels=c("Scenario A", "Scenario B")))
  you_are_here <- you_are_here %>% mutate(scn = "Scenario A") %>%
       bind_rows(you_are_here_b %>% mutate(scn = "Scenario B")) %>%
       mutate(scn_factor = factor(scn, levels=c("Scenario A", "Scenario B")))
  
  pH <- ggplot(d, aes(x = omega_h_pct, y = r_effective, group = scn_factor, color=scn_factor)) +
      geom_line(size=0.8) +
      scale_color_manual(values = c("#4278cf", "#16916c")) +
      geom_point(data=you_are_here, aes(x=x, y=y), pch=21, cex=1.5, stroke=1.25, bg="#ffffff") +
      geom_hline(yintercept=1, lty=2) +
      geom_hline(yintercept=p$R, lwd=0.5) +
      ggtitle("Impact of the completeness of household contact quarantine \non the reproductive number") +
      scale_y_continuous(name = "R", limits = c(min(c(1, d$r_effective)), max(c(d$r_effective, p$R)))) +
      scale_x_continuous(name = "Percent household contacts notified and quarantined") +
      theme_hc() 
  pH
 
  cap <- paste0("**Figure ", fig_counter, "**: Impact of completeness of household contact tracing, as the percent of household contacts notified and quarantined through contact tracing, on the reproductive number, assuming that contacts are isolated on average ", round(p$t_qh, 1), " days after symptom onset of the index case in Scenario A. The filled circles represent the reproductive number for Scenarios A and B, described above. The lines represents the reproductive number if the percent of household contacts notified and quarantined is changed, while all other assumptions for each scenario remain constant. The solid black line represents the reproductive number if there were no contact tracing program, and the dashed black line represents a reproductive number of 1, below which an epidemic would be expected to no longer grow.")
  fig_counter <- fig_counter + 1
  
```

```{r}
if (shiny::isRunning())
  shiny::setProgress(0.5) 
```


```{r hh delay plot, fig.cap=cap, fig.width=6, fig.height=5}

  diff <- p$t_qha - p$t_qhs

  if (p$t_qhs <= p$t_qha) {
    t_qhs <- seq(0, 14, 0.5)
  } else {
    t_qhs <- seq(p$t_qhs - p$t_qha, 14 + (p$t_qhs - p$t_qha), 0.5)
  }

  grid <- expand.grid(
      alpha = p$alpha,
      R = p$R,
      kappa = p$kappa,
      eta = p$eta,
      nu = p$nu,
      t_ps = p$t_ps,
      t_pa = p$t_pa,
      t_qcs = p$t_qcs,
      t_qca = p$t_qca,
      t_qhs = t_qhs,
      t_qha = 1,
      t_q = p$t_q,
      omega_c = p$omega_c,
      omega_h = p$omega_h,
      omega_q = p$omega_q,
      rho_s = p$rho_s,
      rho_a = p$rho_a,
      offset = p$offset,
      shape = as.numeric(p$generation),
      rate = p$rate
    )
  grid <- grid %>%
          mutate(t_qha = t_qhs + diff)
  
  d <- pmap_df(grid, tti:::get_r_effective_df_one)
  d <- d %>%
      mutate(
        t = t_qhs * (1 - alpha) + t_qha * alpha
      )
  
  you_are_here <- tibble(
      x = p$t_qhs * (1 - p$alpha) + p$t_qha * p$alpha,
      y = r_eff(),
      name = "You are here"
    )
  
  
  diff_b <- pB$t_qha - pB$t_qhs

  if (pB$t_qhs <= pB$t_qha) {
    t_qhs_b <- seq(0, 14, 0.5)
  } else {
    t_qhs_b <- seq(pB$t_qhs - pB$t_qha, 14 + (pB$t_qhs - pB$t_qha), 0.5)
  }
    
  grid_b <- expand.grid(
      alpha = pB$alpha,
      R = pB$R,
      kappa = pB$kappa,
      eta = pB$eta,
      nu = pB$nu,
      t_ps = pB$t_ps,
      t_pa = pB$t_pa,
      t_qcs = pB$t_qcs,
      t_qca = pB$t_qca,
      t_qhs = t_qhs_b,
      t_qha = 1,
      t_q = pB$t_q,
      omega_c = pB$omega_c,
      omega_h = pB$omega_h,
      omega_q = pB$omega_q,
      rho_s = pB$rho_s,
      rho_a = pB$rho_a,
      offset = pB$offset,
      shape = as.numeric(p$generation),
      rate = pB$rate
    )
  grid_b <- grid_b %>%
          mutate(t_qha = t_qhs + diff_b)
  

  d_b <- pmap_df(grid_b, tti:::get_r_effective_df_one)
  d_b <- d_b %>%
      mutate(
        t = t_qhs * (1 - alpha) + t_qha * alpha
      )
  
  you_are_here_b <- tibble(
      x = pB$t_qhs * (1 - pB$alpha) + pB$t_qha * pB$alpha,
      y = r_eff(pB),
      name = "You are here"
    )
  
  d <- d %>% mutate(scn = "Scenario A") %>%
       bind_rows(d_b %>% mutate(scn = "Scenario B")) %>%
       mutate(scn_factor = factor(scn, levels=c("Scenario A", "Scenario B")))
  you_are_here <- you_are_here %>% mutate(scn = "Scenario A") %>%
       bind_rows(you_are_here_b %>% mutate(scn = "Scenario B")) %>%
       mutate(scn_factor = factor(scn, levels=c("Scenario A", "Scenario B")))
  
  pHDelay <- ggplot(d, aes(x = t, y = r_effective, group = scn_factor, color=scn_factor)) +
              geom_line(size=0.8) +
              scale_color_manual(values = c("#4278cf", "#16916c")) +
              geom_point(data=you_are_here, aes(x=x, y=y), pch=21, cex=1.5, stroke=1.25, bg="#ffffff") +
              geom_hline(yintercept=1, lty=2) +
              geom_hline(yintercept=p$R, lwd=0.5) +
              ggtitle("Impact of the delay in quarantine of household contacts \non the reproductive number") +
              scale_y_continuous(name = "R", limits = c(min(c(1, d$r_effective)), max(c(d$r_effective, p$R)))) +
              scale_x_continuous(name = "Days from case symptom onset to quarantine of household contacts") +
              theme_hc() 
  pHDelay
 
  cap <- paste0("**Figure ", fig_counter, "**: Impact of timing of household contact tracing, as the delay between symptom onset of the detected case and quarantine of their household contacts, assuming that on average ", round(p$omega_h*100), "% of household contacts are notified and quarantined in Scenario A. The filled circles represent the reproductive number for Scenarios A and B, described above.The lines represents the reproductive number if the average time between case symptom onset and community contact quarantine is changed, while all other assumptions in each scenario remain constant.  The solid black line represents the reproductive number if there were no contact tracing program, and the dashed black line represents a reproductive number of 1, below which an epidemic would be expected to no longer grow.")
  fig_counter <- fig_counter + 1
  
```

### Impact of Community Contact Tracing

```{r c contact plot, fig.cap=cap, fig.width=6, fig.height=5}

  grid <- expand.grid(
      alpha = p$alpha,
      R = p$R,
      kappa = p$kappa,
      eta = p$eta,
      nu = p$nu,
      t_ps = p$t_ps,
      t_pa = p$t_pa,
      t_qcs = p$t_qcs,
      t_qca = p$t_qca,
      t_qhs = p$t_qhs,
      t_qha = p$t_qha,
      t_q = p$t_q,
      omega_c = seq(0, 1, 0.01),
      omega_h = p$omega_h,
      omega_q = p$omega_q,
      rho_s = p$rho_s,
      rho_a = p$rho_a,
      offset = p$offset,
      shape = as.numeric(p$generation),
      rate = p$rate
    )
  
  d <- pmap_df(grid, tti:::get_r_effective_df_one)%>%
        mutate(omega_c_pct = omega_c*100)

  you_are_here <- tibble(
      x = p$omega_c*100,
      y = r_eff(p),
      name = "You are here"
    )

  
  grid_b <- expand.grid(
      alpha = pB$alpha,
      R = pB$R,
      kappa = pB$kappa,
      eta = pB$eta,
      nu = pB$nu,
      t_ps = pB$t_ps,
      t_pa = pB$t_pa,
      t_qcs = pB$t_qcs,
      t_qca = pB$t_qca,
      t_qhs = pB$t_qhs,
      t_qha = pB$t_qha,
      t_q = pB$t_q,
      omega_c = seq(0, 1, 0.01),
      omega_h = pB$omega_h,
      omega_q = pB$omega_q,
      rho_s = pB$rho_s,
      rho_a = pB$rho_a,
      offset = pB$offset,
      shape = as.numeric(p$generation),
      rate = pB$rate
    )
  
  d_b <- pmap_df(grid_b, tti:::get_r_effective_df_one)%>%
        mutate(omega_c_pct = omega_h*100)

  you_are_here_b <- tibble(
      x = pB$omega_c*100,
      y = r_eff(pB),
      name = "You are here"
    )
  
  d <- d %>% mutate(scn = "Scenario A") %>%
       bind_rows(d_b %>% mutate(scn = "Scenario B")) %>%
       mutate(scn_factor = factor(scn, levels=c("Scenario A", "Scenario B")))
  you_are_here <- you_are_here %>% mutate(scn = "Scenario A") %>%
       bind_rows(you_are_here_b %>% mutate(scn = "Scenario B")) %>%
       mutate(scn_factor = factor(scn, levels=c("Scenario A", "Scenario B")))
  
  pC <- ggplot(d, aes(x = omega_c_pct, y = r_effective, group = scn_factor, color=scn_factor)) +
      geom_line(size=0.8) +
      scale_color_manual(values = c("#4278cf", "#16916c")) +
      geom_point(data=you_are_here, aes(x=x, y=y), pch=21, cex=1.5, stroke=1.25, bg="#ffffff") +
      geom_hline(yintercept=1, lty=2) +
      geom_hline(yintercept=p$R, lwd=0.5) +
      ggtitle("Impact of the completeness of community contact quarantine \non the reproductive number") +
      scale_y_continuous(name = "R", limits = c(min(c(1, d$r_effective)), max(c(d$r_effective, p$R)))) +
      scale_x_continuous(name = "Percent community contacts notified and quarantined") +
      theme_hc() 
  pC
 
  cap <- paste0("**Figure ", fig_counter, "**: Impact of completeness of community contact tracing, as the percent of community contacts notified and quarantined through contact tracing, on the reproductive number, assuming that contacts are isolated on average ", round(p$t_qc, 1), " days after symptom onset of the index case. The filled circles represent the reproductive number for Scenarios A and B, described above. The lines represents the reproductive number if the percent of community contacts notified and quarantined is changed, while all other assumptions for each scenario remain constant. The solid black line represents the reproductive number if there were no contact tracing program, and the dashed black line represents a reproductive number of 1, below which an epidemic would be expected to no longer grow.")
  fig_counter <- fig_counter + 1
  
```

```{r c delay plot, fig.cap=cap, fig.width=6, fig.height=5}

  diff <- p$t_qca - p$t_qcs

  if (p$t_qcs <= p$t_qca) {
    t_qcs <- seq(0, 14, 0.5)
  } else {
    t_qcs <- seq(p$t_qcs - p$t_qca, 14 + (p$t_qcs - p$t_qca), 0.5)
  }

  grid <- expand.grid(
      alpha = p$alpha,
      R = p$R,
      kappa = p$kappa,
      eta = p$eta,
      nu = p$nu,
      t_ps = p$t_ps,
      t_pa = p$t_pa,
      t_qcs = t_qcs,
      t_qca = 1,
      t_qhs = p$t_qhs,
      t_qha = p$t_qha,
      t_q = p$t_q,
      omega_c = p$omega_c,
      omega_h = p$omega_h,
      omega_q = p$omega_q,
      rho_s = p$rho_s,
      rho_a = p$rho_a,
      offset = p$offset,
      shape = as.numeric(p$generation),
      rate = p$rate
    )
  grid <- grid %>%
          mutate(t_qca = t_qcs + diff)
  
  d <- pmap_df(grid, tti:::get_r_effective_df_one)
  d <- d %>%
      mutate(
        t = t_qcs * (1 - alpha) + t_qca * alpha
      )
  
  you_are_here <- tibble(
      x = p$t_qcs * (1 - p$alpha) + p$t_qca * p$alpha,
      y = r_eff(),
      name = "You are here"
    )
  
  diff_b <- pB$t_qca - pB$t_qcs

  if (pB$t_qcs <= pB$t_qca) {
    t_qcs_b <- seq(0, 14, 0.5)
  } else {
    t_qcs_b <- seq(pB$t_qcs - pB$t_qca, 14 + (pB$t_qcs - pB$t_qca), 0.5)
  }
    
  grid_b <- expand.grid(
      alpha = pB$alpha,
      R = pB$R,
      kappa = pB$kappa,
      eta = pB$eta,
      nu = pB$nu,
      t_ps = pB$t_ps,
      t_pa = pB$t_pa,
      t_qcs = t_qcs_b,
      t_qca = 1,
      t_qhs = pB$t_qhs,
      t_qha = pB$t_qha,
      t_q = pB$t_q,
      omega_c = pB$omega_c,
      omega_h = pB$omega_h,
      omega_q = pB$omega_q,
      rho_s = pB$rho_s,
      rho_a = pB$rho_a,
      offset = pB$offset,
      shape = as.numeric(p$generation),
      rate = pB$rate
    )
  grid_b <- grid_b %>%
          mutate(t_qca = t_qcs + diff_b)
  
  d_b <- pmap_df(grid_b, tti:::get_r_effective_df_one)
  d_b <- d_b %>%
      mutate(
        t = t_qcs * (1 - alpha) + t_qca * alpha
      )
  
  you_are_here_b <- tibble(
      x = pB$t_qcs * (1 - pB$alpha) + pB$t_qca * pB$alpha,
      y = r_eff(pB),
      name = "You are here"
    )
  
  d <- d %>% mutate(scn = "Scenario A") %>%
       bind_rows(d_b %>% mutate(scn = "Scenario B")) %>%
       mutate(scn_factor = factor(scn, levels=c("Scenario A", "Scenario B")))
  you_are_here <- you_are_here %>% mutate(scn = "Scenario A") %>%
       bind_rows(you_are_here_b %>% mutate(scn = "Scenario B")) %>%
       mutate(scn_factor = factor(scn, levels=c("Scenario A", "Scenario B")))
  
  pHDelay <- ggplot(d, aes(x = t, y = r_effective, group = scn_factor, color=scn_factor)) +
              geom_line(size=0.8) +
              scale_color_manual(values = c("#4278cf", "#16916c")) +
              geom_point(data=you_are_here, aes(x=x, y=y), pch=21, cex=1.5, stroke=1.25, bg="#ffffff") +
              geom_hline(yintercept=1, lty=2) +
              geom_hline(yintercept=p$R, lwd=0.5) +
              ggtitle("Impact of the delay in quarantine of community contacts \non the reproductive number") +
              scale_y_continuous(name = "R", limits = c(min(c(1, d$r_effective)), max(c(d$r_effective, p$R)))) +
              scale_x_continuous(name = "Days from case symptom onset to quarantine of community contacts") +
              theme_hc() 
  pHDelay
 
  cap <- paste0("**Figure ", fig_counter, "**: Impact of timing of community contact tracing, as the delay between symptom onset of the detected case and quarantine of their community contacts, assuming that on average ", round(p$omega_c*100), "% of community contacts are notified and quarantined in Scenario A. The filled circles represent the reproductive number for Scenarios A and B, described above. The lines represents the reproductive number if the average time between case symptom onset and community contact quarantine is changed, while all other assumptions in each scenario remain constant. The solid black line represents the reproductive number if there were no contact tracing program, and the dashed black line represents a reproductive number of 1, below which an epidemic would be expected to no longer grow.")
  fig_counter <- fig_counter + 1
  
```

### Technical Details

We developed a mathematical model to estimate the impact of test-trace-isolate programs on onward disease transmission. We consider transmission in discrete generations from individuals who have been captured in surveillance (V), effectively isolated or quarantined through test and trace efforts (Q), or who remain undetected in the community (C). We consider that, in each generation, some proportion of infections will be detected through a surveillance program. Onward transmission from those individuals ("index cases") is reduced by some factor, dependent on the timing from case identification to isolation and the assumed timing of infectiousness. The contacts of index cases are then able to be enumerated and potentially quarantined; similarly, onward transmission from infected contacts of index cases can be reduced, dependent on the time from index case identification and contact quarantine. We consider differences in the identification of asymptomatic and symptomatic index cases and quarantine of household and community contacts of index cases.

Full details of this model can be found here.  An interactive application implementing this model to explore the effectiveness of contact tracing programs can be found [here](https://iddynamics.jhsph.edu/apps/connect/contessa).

```{r}
if (shiny::isRunning())
  shiny::setProgress(1)  
```

